### 2014-10-08 generic.Rmd
Making the .Rmd output tidier.

# Results from fitting procedure
```{r}
library(pander)
library(ggplot2)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
top_n_bottom <- function(df, k) { # Take the top and bottom k rows
    n = nrow(df)
    if(2*k < n) {
        df[c(1:k,(n-(k-1)):n), ]
    }
    else {
        df
    }
}
counts_table <- function(in_longwin, in_shortwin, half_n_show) {
    if ( in_longwin > longwin(model@counts) || in_shortwin > shortwin(model@counts) ) {
        cat("Window size of counts too small.")
    }
    else {
        resids = computeresids(model,
                in_longwin=in_longwin,
                in_shortwin=in_shortwin,
                in_leftwin=in_shortwin,
                counts=model@counts)
        pandoc.table(top_n_bottom(resids, half_n_show), style="rmarkdown")
    }
}
cat(model@invocation)
```

## Fitted parameter values
```{r, results="asis"}
par_df = data.frame(value = model@results[["par"]], row.names = names(model@results[["par"]]))
pandoc.table(par_df, style="rmarkdown")
par_df$names = row.names(par_df)
par_df = par_df[grep("->", par_df$names),]
ggplot(par_df, aes(x = names, y = value)) +
    geom_bar(stat = "identity", fill="white", color="gray") +
    theme(axis.text.x = element_text(angle = 90))
```

## Window sizes and amount of data used to fit
```{r}
counts <- model@counts@counts
head(counts) # for some reason the code doesn't work if we don't print out some of the counts
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counts)[[1]]),
    "\ntotal counts:", sum(counts))
```

## Result of fitting operation
```{r}
cat("convergence: ", model@results$convergence,
    "\nmessage: ", model@results$message)
```

## residuals for 2-2 Tmers
```{r, results="asis"}
counts_table(in_longwin=2, in_shortwin=2, half_n_show=5)
```

>>>>

# Results from fitting procedure

*Invocation:*
```{r, echo=FALSE}
library(pander)
library(ggplot2)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
top_n_bottom <- function(df, k) { # Take the top and bottom k rows
    n = nrow(df)
    if(2*k < n) {
        df[c(1:k,(n-(k-1)):n), ]
    }
    else {
        df
    }
}
counts_table <- function(in_longwin, in_shortwin, half_n_show) {
    if ( in_longwin > longwin(model@counts) || in_shortwin > shortwin(model@counts) ) {
        cat("Window size of counts too small.")
    }
    else {
        resids = computeresids(model,
                in_longwin=in_longwin,
                in_shortwin=in_shortwin,
                in_leftwin=in_shortwin,
                counts=model@counts)
        pandoc.table(top_n_bottom(resids, half_n_show), style="rmarkdown")
    }
}
cat(model@invocation)
```

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
par_df = data.frame(value = model@results[["par"]], row.names = names(model@results[["par"]]))
pandoc.table(par_df, style="rmarkdown")
par_df$names = row.names(par_df)
par_df = par_df[grep("->", par_df$names),]
ggplot(par_df, aes(x = names, y = value)) +
    geom_bar(stat = "identity", fill="white", color="gray") +
    theme(axis.text.x = element_text(angle = 90))
```

## Window sizes and amount of data used to fit
```{r, echo=FALSE, results="hide"}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counts <- model@counts@counts
head(counts)
```

```{r, echo=FALSE}
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counts)[[1]]),
    "\ntotal counts:", sum(counts))
```

## Result of fitting operation
```{r, echo=FALSE}
cat("convergence: ", model@results$convergence,
    "\nmessage: ", model@results$message)
```

## residuals for 2-2 Tmers
```{r, echo=FALSE, results="asis"}
counts_table(in_longwin=2, in_shortwin=2, half_n_show=5)
```
